NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-10 paper/Chapters/Chapter3.tex
BMI table 2 done

@@

Association between the

@@

	\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults, with or without diabetes. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lccccc}
		\hiderowcolors
		\toprule
		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
		\cmidrule(l{2pt}r{2pt}){2-6}
		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
		\midrule
		\showrowcolors
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0,43 (-1.13, 0.26) & 0.22\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.10 (-0.97, 0.77) & 0.82 & -0.39 (-1.10, 0.31) & 0.269\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.040\\
		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
		\bottomrule
		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition}}\\
		\multicolumn{6}{l}{{\scriptsize  survey rolling programme.}}\\
		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other covariates remained the}}\\
		\multicolumn{6}{l}{{\scriptsize  same with the corresponding Model 1s.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} P values were obtained from wald tests from linear regression models.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total }}\\
		\multicolumn{6}{l}{{\scriptsize  energy intake, alcohol consumption;}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol}}\\ 
		\multicolumn{6}{l}{{\scriptsize  consumption.}}\\
	\end{tabular}
\end{table}
\vspace{-0.3cm}
\rowcolors{2}{white}{white}

>>>>

%\end{table}

@@

Results of the regression analyses showed inverse associations between latent classes of carbohydrate eating patterns and BMI among men \textbf{(Table \ref{tab:tab2BMI})}. However, the 95\%CI of the regression coefficients were all too wide and including the null value 0, indicating no statistically supported evidence of the association. Nonetheless, evidence of interaction effect of whether live a partner or not on the association between carbohydrate eating patterns and BMI was found (\textit{p} = 0.014 and 0.036 for women in total and women without diabetes). For women living with her partner, latent classes of carbohydrate eating patterns were negatively associated with BMI.

@@

	\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults, with or without diabetes. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lccccc}
		\hiderowcolors
		\toprule
		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
		\cmidrule(l{2pt}r{2pt}){2-6}
		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
		\midrule
		\showrowcolors
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0.43 (-1.13, 0.26) & 0.220\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.10 (-0.97, 0.77) & 0.820 & -0.39 (-1.10, 0.31) & 0.269\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.040\\
		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
		\bottomrule
		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition}}\\
		\multicolumn{6}{l}{{\scriptsize  survey rolling programme.}}\\
		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other covariates remained the}}\\
		\multicolumn{6}{l}{{\scriptsize  same with the corresponding Model 1s.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from linear regression models.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total }}\\
		\multicolumn{6}{l}{{\scriptsize  energy intake, alcohol consumption;}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol}}\\ 
		\multicolumn{6}{l}{{\scriptsize  consumption.}}\\
	\end{tabular}
\end{table}
\vspace{-0.3cm}
\rowcolors{2}{white}{white}

Comparing with women eating low carbohydrate meals, women having a high carbohydrate eating pattern was averagely associated with 1.76 kg/m\textsuperscript{2} lower BMI. 95\%CI for the difference was 0.73 to 2.78 kg/m\textsuperscript{2}, \textit{p} = 0.001. After excluding diabetic women, BMI was still 1.62 kg/m\textsuperscript{2} (95\%CI: 0.58, 2.65, \textit{p} = 0.002) lower in high carbohydrate eaters versus low carbohydrate eaters on average. On the contrary, latent classes of carbohydrate eating patterns were positively associated with women who lived alone, although the regression coefficients were not statistically different from 0.
